Linear and modal analysis applying the FE$^2$ multi-scale method for composite materials.

### 2018-02-14 article.tex
adding periodic boundary conditions ms

\usepackage{amsmath, amsfonts, amsthm, mathrsfs, bm}
\usepackage{siunitx} \sisetup{retain-zero-exponent}
\usepackage{standalone}
\usepackage{tikz}
\usetikzlibrary{matrix, chains, backgrounds, calc, shapes, arrows, arrows.meta, fit, positioning}
\usepackage{pgfplots, pgfplotstable}
\usepackage{xcolor}
\usepackage{subcaption}
\captionsetup[subfigure]{labelformat = parens, labelsep = space, font = small}

@@

\journal{Journal of \LaTeX\ Templates}

@@

%\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
\title{Linear and modal analysis applying the FE$^2$ multi-scale method for composite materials.}

%% Group authors per affiliation:
%\author{Elsevier\fnref{myfootnote}}
%\address{Radarweg 29, Amsterdam}
%\fntext[myfootnote]{Since 1880.}
\author[bsc]{Guido Giuntoli}
%\address{Carrer Jordi Girona 29, Barcelona}
\author[bsc]{Mariano V\'azquez}
%\address{Carrer Jordi Girona 29, Barcelona}
\author[upc]{Sergio Oller}
%\address{Carrer Jordi Girona 29, Barcelona}
\address[bsc]{River Valley Technologies, SJP Building, Cotton Hills, Trivandrum, Kerala, India 695014}
\address[upc]{River Valley Technologies, SJP Building, Cotton Hills, Trivandrum, Kerala, India 695014}

%\fntext[myfootnote]{\ead[url]{guido.bsc.elisya.org}}

%% or include affiliations in footnotes:
%\author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
%\ead[url]{http://guido.bsc.elisya.org}

%\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
%\cortext[mycorrespondingauthor]{Corresponding author}
%\ead{support@elsevier.com}

%\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
%\address[mysecondaryaddress]{360 Park Avenue South, New York}

%---------------------------------------------------------------------------------------------------
\begin{abstract}
We study the homogenization method with \emph{uniform strains} boundary
conditions in 2D composite material problems.
We assume linear materials and small deformations approach.
Two examples are solved including both: a linear response calculation (force
\emph{vs.} displacement relation) and a modal calculation of the eigenvalues 
of the system, the last ones are directly related with the natural oscillations 
frequencies of the system.
All the problems are compared with the micro-model and with other homogenization 
theories such as the parallel and serial rule of mixtures.
A detail explanation about the computational implementation of the algorithm using 
the finite element method is given.
\end{abstract}

@@

% <figure multi-scale scheme>
\begin{figure}[!ht]
\resizebox{8cm}{!}{\input{figures/multiscale.tikz}}
\caption{\label{fig:multi-scale}Simplified scheme of a multi-scale calculation 
where at the left we have an homogenized macro-structure and 
in the right we have a representative volume element (\emph{r.v.e.}) 
representing the micro-structure.}
\end{figure}

@@

% Master elements
\begin{figure}[!ht]
\begin{minipage}[b]{0.4\linewidth}
\subcaptionbox{\label{fig:tria_master}}{
\resizebox{4.0cm}{!}{\input{figures/tria_master.tikz}}}
\end{minipage}
\hspace{1.5cm}
\begin{minipage}[b]{0.4\linewidth}
\subcaptionbox{\label{fig:quad_master}}{
\resizebox{4.0cm}{!}{\input{figures/quad_master.tikz}}}
\end{minipage}
\caption{Master element to perform the FEM integrals.
a) Master triangle element. 
b) Master quadrangle element.
}
\label{fig_dist_scheme}
\end{figure}

@@

\begin{equation}
\begin{bmatrix}
\frac{\bm{f}_a}{d\bm{u}_a} & \frac{\bm{f}_a}{d\bm{u}_+} & \frac{\bm{f}_a}{d\bm{u}_-}\\
\frac{\bm{f}_b^+ + \bm{f}_b^-}{d\bm{u}_a} & \frac{\bm{f}_b^+ + \bm{f}_b^-}{d\bm{u}_+} & \frac{\bm{f}_b^+ + \bm{f}_b^-}{d\bm{u}_-}\\
\end{bmatrix}
\cdot
\begin{bmatrix}d\bm{u}_a \\ d\bm{u}_- \\ d\bm{u}_-\end{bmatrix}
=
\begin{bmatrix}\bm{f}_a(\bm{u}^{k-1}) \\ \bm{f}_b^+(\bm{u}^{k-1}) + \bm{f}_b^-(\bm{u}^{k-1}) \end{bmatrix}
\end{equation}

@@

>>>>

\usepackage{amsmath, amsfonts, amsthm, mathrsfs, bm, bbm}
\usepackage{siunitx} \sisetup{retain-zero-exponent}
\usepackage{standalone}
\usepackage{tikz}
\usetikzlibrary{matrix, chains, backgrounds, calc, shapes, arrows, arrows.meta, fit, positioning}
\usepackage{pgfplots, pgfplotstable}
\usepackage{xcolor}
\usepackage{subcaption}
\captionsetup[subfigure]{labelformat = parens, labelsep = space, font = small}

@@

\journal{Computer Methods in Applied Mechanics and Engineering.}

@@

\title{Linear and modal analysis applying the FE$^2$ multi-scale method for composite materials.}

%\author{Elsevier\fnref{myfootnote}}
%\fntext[myfootnote]{Since 1880.}
%\address{Carrer Jordi Girona 29, Barcelona}
\author[bsc]{Guido Giuntoli}
\author[bsc]{Mariano V\'azquez}
\author[upc]{Sergio Oller}
\address[bsc]{Barcelona Supercomputing Center, Barcelona, Spain}
\address[upc]{Universitat Polit\`ecnica de Catalunya, Barcelona, Spain}

\begin{abstract}
We study the homogenization method with \emph{uniform strains} boundary
conditions in 2D composite material problems.
We assume linear materials and small deformations approach.
Two examples are solved including both: a linear response calculation (force
\emph{vs.} displacement relation) and a modal calculation of the eigenvalues 
of the system, the last ones are directly related with the natural oscillations 
frequencies of the system.
All the problems are compared with the micro-model and with other homogenization 
theories such as the parallel and serial rule of mixtures.
A detail explanation about the computational implementation of the algorithm using 
the finite element method is given.
\end{abstract}

@@

% <figure multi-scale scheme>
\begin{figure}[!ht]
\centering
\resizebox{8cm}{!}{\input{figures/multiscale.tikz}}
\caption{\label{fig:multi-scale}Simplified scheme of a multi-scale calculation 
where at the left we have an homogenized macro-structure and 
in the right we have a representative volume element (\emph{r.v.e.}) 
representing the micro-structure.}
\end{figure}

@@

% Master elements
\begin{figure}[!ht]
\centering
\begin{minipage}[b]{0.4\linewidth}
\subcaptionbox{\label{fig:tria_master}}{
\resizebox{4.0cm}{!}{\input{figures/tria_master.tikz}}}
\end{minipage}
\hspace{1.5cm}
\begin{minipage}[b]{0.4\linewidth}
\subcaptionbox{\label{fig:quad_master}}{
\resizebox{4.0cm}{!}{\input{figures/quad_master.tikz}}}
\end{minipage}
\caption{Master element to perform the FEM integrals.
a) Master triangle element. 
b) Master quadrangle element.
}
\label{fig_dist_scheme}
\end{figure}

@@

\begin{equation}
\begin{bmatrix}
\frac{\bm{f}_a}{d\bm{u}_a} & \frac{\bm{f}_a}{d\bm{u}_+} & \frac{\bm{f}_a}{d\bm{u}_-}\\
\frac{\bm{f}_b^+ + \bm{f}_b^-}{d\bm{u}_a} & \frac{\bm{f}_b^+ + \bm{f}_b^-}{d\bm{u}_+} & \frac{\bm{f}_b^+ + \bm{f}_b^-}{d\bm{u}_-}\\
\end{bmatrix}
\cdot
\begin{bmatrix}d\bm{u}_a \\ d\bm{u}_- \\ d\bm{u}_-\end{bmatrix}
=
\begin{bmatrix}
\bm{f}_a(\bm{u}) \\
\bm{f}_b^+(\bm{u}) + \bm{f}_b^-(\bm{u})
\end{bmatrix}^{k-1}
\end{equation}

@@

\begin{equation}
\left\{
\begin{array}{ll}
\bm{f}_a(\bm{u}) = \bm{0} \\
\bm{f}_b^+(\bm{u}) + \bm{\lambda} = \bm{0} \\
\bm{f}_b^-(\bm{u}) - \bm{\lambda} = \bm{0} \\
\bm{u}^+ - \bm{u}^- - \bm{c} = \bm{0}\\
\end{array}
\right.
\end{equation}

\begin{equation}
\begin{bmatrix}
\frac{\partial\bm{f}_a}{\partial\bm{u}_a} & \frac{\partial\bm{f}_a}{\partial\bm{u}_+} & \frac{\partial\bm{f}_a}{\partial\bm{u}_-} &  \bm{0}\\
\frac{\partial\bm{f}_+}{\partial\bm{u}_a} & \frac{\partial\bm{f}_+}{\partial\bm{u}_+} & \frac{\partial\bm{f}_+}{\partial\bm{u}_-} &  \mathbbm{1}\\
\frac{\partial\bm{f}_-}{\partial\bm{u}_a} & \frac{\partial\bm{f}_-}{\partial\bm{u}_+} & \frac{\partial\bm{f}_-}{\partial\bm{u}_-} & -\mathbbm{1}\\
\bm{0}                                    & \mathbbm{1}                               & -\mathbbm{1}                              &  \bm{0}\\
\end{bmatrix}^{k-1}
\cdot
\begin{bmatrix}
d\bm{u}_a \\
d\bm{u}_+ \\
d\bm{u}_- \\
d\bm{\lambda}
\end{bmatrix}^{k}
=
\begin{bmatrix}
\bm{f}_a(\bm{u}) \\
\bm{f}_b^+(\bm{u}) + \bm{\lambda} \\
\bm{f}_b^-(\bm{u}) - \bm{\lambda} \\
\bm{u}^{+} - \bm{u}^{-} - \bm{c}
\end{bmatrix}^{k-1}
\end{equation}

\begin{equation}
\begin{bmatrix}
\bm{u}_a \\
\bm{u}_+ \\
\bm{u}_- \\
\bm{\lambda}
\end{bmatrix}^{k}
= 
\begin{bmatrix}
\bm{u}_a \\
\bm{u}_+ \\
\bm{u}_- \\
\bm{\lambda}
\end{bmatrix}^{k-1}
+
\begin{bmatrix}
d\bm{u}_a \\
d\bm{u}_+ \\
d\bm{u}_- \\
d\bm{\lambda}
\end{bmatrix}^{k-1}
\end{equation}
